Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-03-09 RR_manuscript/Draft_RR.Rmd
jvc edits

In this article, we will investigate the variability in analytic choices when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the operationalization of a complex  signal and decisions regarding the statistical analysis.
<!-- TODO: include number of teams when known -->
Specifically, we will report the impact of analytic decision on research results obtained by a minimum of 12 teams who will gain access to the same set of acoustic recordings in order to answer the same research question.
<!-- TODO: check tense throughout, should be future tense -->

@@

Data analysis comes with many decisions like how to measure a given phenomenon or behavior, what data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision procedure to apply.
This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
Humans filter the world in irrational ways [e.g., @tversky1974judgment], seeing coherent patterns in randomness [@brugger2001], convincing themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceiving events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
In connection with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytical pipelines, but only reporting a select few.
This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways to measure [@roettger2019researcher].
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility [e.g. miguel2014promoting; @klein2018practical] and freely available and accessible infrastructures such as provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still not very common because data sharing remains rare [@wicherts2006poor].

While analytical flexibility has been widely discussed both from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and its application in individual scientific fields [e.g. Wichert et al. 2015, Charles et al. 2019, @roettger2019researcher], there are still many unknowns regarding the extent of analytical plurality in practice.
<!-- TODO: add refs for wichert et al. 2015, Charles et al. 2019 -->

Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability.

@@

In a collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis.
Analytical approaches and consequently the results varied widely between teams.
Sixty-nine percent of the teams found support for the hypothesis, and 31% did not.
Out of the 29 analytical strategies, there were 21 unique combinations of covariates.
Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
The authors results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias.

@@

While these studies attested a large degree of analytical flexibility with possibly impactful consequences, they only investigated analytical decisions related to inferential statistics or the architecture of computational models.
In these studies the data sets were fixed and data collection or measurement could not be changed.

However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
This is especially true in the social sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.
Decisions about how to measure a theoretical construct related to such behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.
For example, @flake2020 discuss the cascading impact that different practices can have on psychometric research.
The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
Taken together, these aspects alone exponentially increase the combinations of possible analytical choices, and hence flexibility in research outcomes.

In those social sciences concerned with communication, human behaviour is sometimes measured as a complex visual or acoustic signal.
<!-- TODO: check BE vs. AE -->
This added complexity introduces further fork junctions in the research pipe-line, and in turn further increases analytical flexibility.
The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where complex decision procedures are involved in the operationalization and measuring of complex signals.

@@

Research on speech is at the heart of the cognitive sciences, informing psychological models of language, categorization, and memory, guiding methods for diagnosis and therapy of speech disorders, and facilitating advancement in automatic speech recognition and speech synthesis.
One major challenge in the speech sciences is the mapping between communicative intentions (the unobserved behavior) and their physical manifestation (the observed behaviour).

@@

Speech categories are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
The acoustic parameters of one category are usually asynchronous, i.e. they appear at different time points in the unfolding signal, and overlap with parameters of other categories [e.g. @jongman2000acoustic; @lisker1986voicing; Summerfield, 1984; @winter2014spoken].
<!-- TODO: add summerfield ref-->
A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs *pear*).
This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid].
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/t, d/) [@hawkins2004influence].

The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
For example, studies investigating acoustic correlates of word stress (e.g. the difference between *insíght* and *íncite*) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) [e.g., @gordon2017acoustic].
Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g. Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations [@heuven2002], as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].
Extra-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch [@foulkes2006; @ogden2004; @white2009].

When testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
The larger the functional domain (e.g. segments vs words vs utterances), the higher the number of conceivable operationalizations.
For example, several decisions have to be made when comparing the two realization of the sentence in (1), one of which is intended to signal emphasis on *another* and one of which emphasizes *zoom*.

@@

When looking at phrase-level temporal domains, the number of possible analytical pipelines quickly explodes.
This plurality of analytical paths is illustrated in Figure \@ref(fig:forkingPaths).
When comparing two utterance such as (2a) and (2b), there are many things to consider.
Even if we have decided to compare fundamental frequency (f0) of only the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
For example, we could measure f0 at specific points in time like the onset of the window, the offset, or the midpoint.
We could also measure the value or time of the minimum or maximum f0 value.
We could summarise f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyse speech data [see @gordon2017acoustic].
And the garden of forking paths does not stop here.
<!-- TODO: add examples of pitch tracking options -->
In \highlight[id=SC, comment = {The figure text is quite small. Probably better to change to a longer rather then wider layout.}][id=TR, comment = {Better now?}]{Figure} \@ref(fig:forkingPaths), we went with a specific option to automatically calculate f0, INSERT SOME EXAMPLES OF PITCH TRACKING OPTIONS.\comment{add examples of pitch tracking options}
Moreover, knowing that the signals and the measures thereof can be noisy, we could smooth these using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on.

@@

## The data set: The acoustic properties of atypical modifiers
Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy [@grice1975logic].
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective *yellow* to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

@@

Even looking at morphosyntactically identical expressions, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved [e.g., @ladd2008intonational].
Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
Intonation marks discourse-relevant referents for being new or given information to guide the listeners’ interpretation of incoming messages. 
Beyond structuring information relative to the discourse, a few studies suggested that speakers might use intonation to signal atypical lexical combinations [e.g. dimitrova2008prosodic; dimitrova2009did]. 
Referential expressions such as *blue banana* were produced with greater prosodic prominence than more typical referent such as *yellow banana*.
If true, these findings are in line with the idea of resource-efficient, rational language users who modulate their speech in order to facilitate listeners' comprehension process.
However, the original conclusions of above studies were based on small (n=10), unjustified sample sizes. 
Moreover, the data is not available, and the statistical analysis uses anti-conservative co-variance structures, lending reasonable doubt on the original conclusions.

@@

To further illuminate the question of whether speakers modify speech to signal atypical referents, we recorded thirty native German speakers interacting with a confederate (one of the experimenters) in a referential game.
The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
The participant and the experimenter could not see each other nor each others' screens.
After a familiarisation phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.

<!-- TODO: see XXX, what do we refer to here? -->

@@

# Methods
As outlined in Section \@ref(s:operspeech), researchers are faced with a large amount of analytical choices when analyzing a multidimensional signal such as speech.
Analyst must identify relevant measurements as well as temporal domain(s) from within which these measures are to be taken, operationalize and possibly transform those measures, before submitting them to statistical models, which have to be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytical flexibility that social science might face across disciplines.
We will take on a meta-analytical approach to assess (i) the variability of the reported effects, and (ii) and how analytical and demographic factors affect the researchers' final results.

<!-- QUESTION: wanna meditate over the term demographic-->

@@

<!-- TODO: add materials link and mailing lists -->
The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project (LINK) and a short pre-recorded slide show that summarizes the study and research question (LINK).
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer to single researcher or small teams as "analysis teams".

Recruitment for this project is ongoing but we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).

<!-- QUESTION: How to frame this sentence. It is not ongoing. Alternatively: "Recruitment for this project will commence as soon as the present Registered Report is in-principle accepted.-->

@@

<!-- TODO: add citation to ECO RR -->
To identify the minimal sample size, we followed the method in Parker et al. \highlight{[ECO RR]}.
The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e. the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity. 
We consider a posterior distribution of $\tau^2$, for which the 95% credible interval (CrI) does not include 0 as sufficient (i.e. the probability $p$ that the 95% CrI contains 0 should be less than 0.05).
<!-- QUESTION: the sentence in brackets looks wrong, this would be true for confidence intervals right? -->
The probability $p$ that a CrI interval does not include 0 is obtained via the *t*-statistics:

@@

where $n$ is the sample size.
Since we know $p$ and $\tau^2$, we can calculate $n$ such that $p < 0.05$.
Inserting $SE(\tau^2)$ into the formula of the *t*-statistics shows that, when $n$ is fixed, *t* (and hence $p$) will be the same regardless of $\tau^2$:

@@

<!-- TODO: add link to analytical survey -->
Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanations of their analytical choices, their quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.

@@

The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code and the data set.
<!-- TODO: add link to peer review survey -->
The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
To help reviewers calibrate their rating, they will be given the following guidelines:

@@

The reviewers will also be given the option to include further comments in text box for each of the three ratings.

After submitting the review, a methods section from a second analysis will then be made available to the reviewer.
This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide for an explanation.

@@

We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g. f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g. mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects [if applicable], (d) the nature and reasoning behind inferential assessments (e.g. dichotomous decision based on *p*-values, ordinal decision based on Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the reported effect sizes.
<!-- QUESTION: range of the standardized effect sizes, right? -->

@@

To summarize the variability in reported effect sized, we will follow Bayesian random-effects meta-analytical \highlight[id=SC, comment={It would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model}]{techniques}.
Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, so that common effect size measures such as Cohen's $d$ would be inappropriate.
Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Herz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e. the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each factor variable will be decided on a model-by-model basis, depending on which levels were compared by the team.
<!-- TR: don't know what you mean tbh -->
Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.

The estimated coefficients of the critical predictors (i.e. critical according to the analysis teams' self-reported inferential criteria), as obtained from the standardized models, will be used as the standardized effect size ($\eta_i$) of each reported model.
If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytical model (described in details in the next paragraph).
Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the standard error ($\text{se}_i$) of the effect size.
This will enable us to fit a so-called "measurement-error" model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytical model.
As a desired consequence, effect sizes with a greater standard error will be weighted less than those with a smaller standard error in the meta-analytical calculations.

>>>>

In this article, we will investigate the variability in analytic choices when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the operationalization of a complex  signal and decisions regarding the statistical analysis.
<!-- TODO: include number of teams when known -->
Specifically, we will report the impact of analytic decision making on research results obtained by a minimum of 12 teams who will gain access to the same set of acoustic recordings in order to answer the same research question.
<!-- TODO: check tense throughout, should be future tense -->

@@

Data analysis comes with many decisions, like how to measure a given phenomenon or behavior, which data to submit to statistical modeling and which to exclude in the final analysis, or what inferential decision making procedure to apply.
This can be problematic because humans show cognitive biases that can lead to erroneous inferences.
Humans filter the world in irrational ways [e.g., @tversky1974judgment], seeing coherent patterns in randomness [@brugger2001], convincing themselves of the validity of prior expectations ["I knew it", @nickerson1998confirmation], and perceiving events as being plausible in hindsight ["I knew it all along", @fischhoff1975hindsight].
In conjunction with an academic incentive system that rewards certain discovery processes more than others [@sterling1959publication; @koole2012rewarding], we often find ourselves exploring many possible analytical pipelines, but only reporting a select few. <!-- in connection with = referring to; in conjunction with = together, coupled with. I think we want the later, but change if I'm mistaken (JVC) --> 
This issue is particularly amplified in fields in which the raw data lend themselves to many possible ways of being measured [@roettger2019researcher].
Combined with a wide variety of methodological and theoretical traditions as well as varying levels of statistical training across subfields, the inherent flexibility of data analysis might lead to a vast plurality of analytic approaches that can lead to different scientific conclusions.
Consequently, there might be many published papers that present overconfident interpretations of their data based on idiosyncratic analytic strategies [e.g., @simmons2011false; @gelman2014statistical].
These interpretations are either associated with an unknown amount of uncertainty or lend themselves to alternative interpretation if analyzed differently.
However, instead of being critically evaluated, scientific results often remain unchallenged in the publication record.
Despite recent efforts to improve transparency and reproducibility [e.g. miguel2014promoting; @klein2018practical] and the advent of freely available and accessible infrastructures, such as those provided by the Open Science Framework (osf.io), critical re-analyses of published analytic strategies are still uncommon because data sharing remains rare [@wicherts2006poor].

Analytical flexibility has been widely discussed from a conceptual point of view [@simmons2011false; @wagenmakers2012agenda; @nosek2014method] and in regard to its application in individual scientific fields [e.g. Wichert et al. 2015, Charles et al. 2019, @roettger2019researcher], notwithstanding, there are still many unknowns regarding the extent of analytical plurality in practice.
<!-- TODO: add refs for wichert et al. 2015, Charles et al. 2019... are we certain this isn't @wicherts2016? (JVC) -->
Recent collaborative attempts have started to shed light on how different analysts tackle the same data set and have revealed a large amount of variability. <!-- I think this should be part of the previous paragraph. -->

@@

In a collaborative effort, @silberzahn2018many let twenty-nine independent analysis teams address the same research hypothesis.
Analytical approaches and consequently the results varied widely between teams.
Sixty-nine percent of the teams found support for the hypothesis, and 31% did not.
Out of the 29 analytical strategies, there were 21 unique combinations of covariates.
Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
The authors results suggest that analytic plurality may be an inevitable byproduct of the scientific process and not necessarily driven by different levels of expertise nor bias.

@@

While these studies attested a large degree of analytical flexibility with possibly impactful consequences, they only investigated analytical decisions related to inferential statistics or the architecture of computational models.
In these studies the data sets were fixed and neither data collection nor measurement could be changed.
However, in many fields the primary raw data are complex signals that need to be operationalized relative to a theoretically motivated research question.
This is especially true in the social sciences, where the phenomenon under investigation corresponds to both observable and unobservable human behavior.
Decisions about how to measure a theoretical construct related to such behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa.

For instance, @flake2020 discuss the cascading impact that different practices can have on psychometric research.
The authors highlight, among others, the following degrees of freedom in the choice and development of measures: definition of the theoretical construct, justification of the selected measure, description of the measure and of how it maps onto the construct, response coding and related transformations, and post-hoc modifications to the chosen measure.
Taken together, these aspects alone exponentially increase the combinations of possible analytical choices, and hence flexibility in research outcomes.

In social sciences concerned with communication, human behavior is sometimes measured as a complex visual or acoustic signal.
This added complexity introduces further fork junctions in the research pipe-line, and in turn further increases analytical flexibility.
The present study looks at experimentally elicited speech production data in order to understand how this flexibility manifests itself in a scenario where complex decision procedures are involved in the operationalization and measuring of complex signals.

@@

Research on speech is at the heart of the cognitive sciences, informing psychological models of language, categorization, and memory, guiding methods for diagnosis and therapy of speech disorders, and facilitating advancement in automatic speech recognition and speech synthesis.
One major challenge in the speech sciences is the mapping between communicative intentions (the unobserved behavior) and their physical manifestation (the observed behavior).

@@

Speech categories are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
The acoustic parameters of one category are usually asynchronous, i.e. they appear at different time points in the unfolding signal, and overlap with parameters of other categories [e.g. @jongman2000acoustic; @lisker1986voicing; Summerfield, 1984; @winter2014spoken].
<!-- TODO: add summerfield ref-->
A classical example is the distinction between voiced and voiceless stops in English (i.e. /b/ and /p/ in *bear* vs *pear*).
This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds [@lisker1977rapid]. <!-- why not "phonological contrast"? --> 
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
For example, the initial /l/ of the English words *led* and *let* is affected by the voicing of the final consonant (/t, d/) [@hawkins2004influence].

The multiplicity of phonetic cues grows exponentially if we look at larger temporal domains as is the case for suprasegmental aspects of speech.
For example, studies investigating acoustic correlates of word stress (e.g. the difference between *ínsight* and *incíte*) have been using a wide variety of measurements, including temporal characteristics (duration of certain segments or sub-segmental intervals), spectral characteristics (intensity, formants, and spectral tilt), and measurements related to fundamental frequency (f0) [e.g., @gordon2017acoustic].
Moving on to the expression of higher-level functions, like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances [e.g., @ladd2008intonational].
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g. Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations [@heuven2002], as well as acoustic information within the temporal or spectral domain [e.g., @van2005speech].
Extra-linguistic information, like the speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain parameters, such as voice quality, rhythm, and pitch [@foulkes2006; @ogden2004; @white2009].

In short, when testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
The larger the functional domain (e.g. segments vs words vs utterances), the higher the number of conceivable operationalizations.
For example, several decisions have to be made when comparing the two realization of the sentence in (1), one of which is intended to signal emphasis on *another* and one of which emphasizes *zoom*.

@@

When looking at phrase-level temporal domains, the number of possible analytical pipelines increases exponentially. <!-- this is hyperbole, but seems (possibly) more appropriate than "explodes" -->
This plurality of analytical paths is illustrated in Figure \@ref(fig:forkingPaths).
<!-- When comparing two utterances such as (2a) and (2b), there are many things to consider.  (I think we can do without this sentence.) -->
Even if we have decided to compare fundamental frequency (f0) of only the word *another* across the two utterances, there are still many choices to be made, all of which need to be justified.
For example, we could measure f0 at specific points in time like the onset of the window, the offset, or the midpoint.
We could also measure the value or time of the minimum or maximum f0 value.
We could summarize f0 across the entire window and extract the mean, median or standard deviation of f0, all of which have been used to analyze speech data [see @gordon2017acoustic].
And the garden of forking paths does not stop here.
<!-- TODO: add examples of pitch tracking options -->
Figure \@ref(fig:forkingPaths) \highlight[id=SC, comment = {The figure text is quite small. Probably better to change to a longer rather then wider layout.}]\highlight[id=TR, comment = {Better now?}], illustrates a specific option to automatically calculate f0\highlight[id=TR, comment = {add examples of pitch tracking options}.
Knowing that the signals and the measures thereof can be noisy, another option would be to smooth them using one algorithm and degree over others, or remove values that substantially deviate from surrounding values or expectations, either manually or automatically, and so on. <!-- Im having a bit of trouble with this sentence. I tried to fix it and now I am realizing I don't quite follow (JVC) -->

@@

## The data set: The acoustic properties of atypical modifiers

Referring is one of the most basic and prevalent uses of language and one of the most widely researched areas in language science.
It is an open question how speakers choose a referring expression when they want to refer to a specific entity like a banana.
The context within which an entity occurs (i.e., with other non-fruits, other fruits, or other bananas) plays a large part in determining the choice of referring expressions.
Generally, speakers aim to be as informative as possible to uniquely establish reference to the intended object, but they are also resource-efficient in that they avoid redundancy [@grice1975logic].
Thus one would expect the use of a modifier, for example, only if it is necessary for disambiguation.
For instance, one might use the adjective *yellow* to describe a banana in a situation in which there is a yellow and a less ripe green banana available, but not when there is only one banana to begin with.

@@

Even looking at morphosyntactically identical expressions, speakers can modulate utterances via suprasegmental acoustic properties like temporal and spectral modifications of the segments involved [e.g., @ladd2008intonational].
Most prominently, languages use intonation to signal discourse relationships between referents (among other functions).
Intonation marks discourse-relevant referents for being new or given information to guide the listeners’ interpretation of incoming messages. 
Beyond structuring information relative to the discourse, a few studies suggested that speakers might use intonation to signal atypical lexical combinations [e.g. dimitrova2008prosodic; dimitrova2009did]. 
Referential expressions such as *blue banana* were produced with greater prosodic prominence than more typical referent such as *yellow banana*.
If true, these findings are in line with the idea of resource-efficient, rational language users who modulate their speech in order to facilitate listeners' comprehension process.
However, the original conclusions of above studies were based on small (n=10), unjustified sample sizes. 
Moreover, the data is not available, and the statistical analysis used anti-conservative co-variance structures, leaving reason to doubt the original conclusions. <!-- "lending doubt on" sounded a bit weird to me (JVC) -->

@@

To further illuminate the question of whether speakers modify speech to signal atypical referents, we recorded thirty native German speakers interacting with a confederate (one of the experimenters) in a referential game.
The participants had to verbally instruct the confederate to select a specified target object out of four object presented on a screen.
The subject and confederate were seated at the opposite sides of a table, each facing one of two mirrored computer screens.
The participant and the experimenter could not see each other nor each others' screens.
After a familiarization phase (see XXX), the subject first saw four colored objects in the top left, top right, bottom left, and bottom right corners of the screen.

<!-- TODO: see XXX, what do we refer to here? Are we going to include an image? -->

@@

# Methods

As outlined in Section \@ref(s:operspeech), researchers are faced with a large amount of analytical choices when analyzing a multidimensional signal such as speech.
Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytical flexibility that social science might face across disciplines.
We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) and how analytic and demographic factors affect the researchers' final results.

<!-- QUESTION: wanna meditate over the term demographic (add analytic vs. analytical too)-->

@@

<!-- TODO: add materials link and mailing lists -->
The initiating authors (SC, JC, TR) created an online landing page providing a general description of the project [https://many-speech-analyses.github.io](https://many-speech-analyses.github.io) and a short pre-recorded slide show that summarizes the study and research question (LINK). <!-- same as above, or OSF -->
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer to single researcher or small teams as "analysis teams".

Recruitment for this project will commence upon receiving in-principle acceptance; we aim for a minimum of 12 analysis teams independently evaluating each data set (see sample size justification below).

<!-- QUESTION: How to frame this sentence. It is not ongoing. Alternatively: "Recruitment for this project will commence as soon as the present Registered Report is in-principle accepted. (This seems good to me. added) -->

@@

<!-- TODO: add citation to ECO RR -->
Following Parker et al. \highlight{[ECO RR]}, we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e. the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity. 
We consider a posterior distribution of $\tau^2$, for which the 95% credible interval (CrI) does not include 0 as sufficient (i.e. the probability $p$ that the 95% CrI contains 0 should be less than 0.05).
<!-- QUESTION: the sentence in brackets looks wrong, this would be true for confidence intervals right? -->
The probability $p$ that a CrI interval does not include 0 is obtained via the *t*-statistic:

@@

where $n$ is the sample size.
Given $p$ and $\tau^2$, we can calculate $n$ such that $p < 0.05$.
Inserting $SE(\tau^2)$ into the formula for the *t*-statistic shows that, when $n$ is fixed, *t* (and hence $p$) will be the same regardless of $\tau^2$:

@@

<!-- TODO: add link to analytical survey -->
Once their analysis is complete, they will answer a structured survey (LINK), providing information about their analysis technique, an explanation of their analytical choices, their quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready statistical methods section.

@@

The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team's answers to our survey questions regarding their methods, including analysis code and the data set.
<!-- TODO: add link to peer review survey -->
The reviewer will then be asked in an online survey (LINK) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
To help reviewers calibrate their rating, they will be given the following guidelines:

@@

The reviewers will also be given the option to include further comments in a text box for each of the three ratings.

After submitting the review, a methods section from a second analysis will then be made available to the reviewer.
This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.

@@

We will calculate summary statistics describing variation among analyses, including (a) the nature and number of acoustic measures (e.g. f0 or duration), (b) the operationalization and the temporal domain of measurement (e.g. mean of an interval or value at specified point in time), (c) the nature and number of model parameters for both fixed and random effects [if applicable], (d) the nature and reasoning behind inferential assessments (e.g. dichotomous decision based on *p*-values, ordinal decision based on a Bayes factor), as well as the (e) mean, (f) standard deviation and (g) range of the reported effect sizes.
<!-- QUESTION: range of the standardized effect sizes, right? -->

@@

We will summarize the variability in reported effect sizes using Bayesian meta-analytic \highlight[id=SC, comment={It would be good to decide on a clear terminology to refer to the individual original models, the individual models that we run (to refit the original models), and the meta-analytical model}]{techniques}.
Based on the common practices currently in place within the field, we anticipate that researchers will use multi-level/hierarchical/random-effects regression models, thus common measurements of effect size, such as Cohen's $d$, may be inappropriate.
Since the variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hertz for frequency vs milliseconds for duration), we will standardize all reported effects by refitting each reported model with centered and scaled continuous variables (*z*-scores, i.e. the observed values subtracted from the mean divided by the standard deviation) and sum-coded factor variables.
\highlight[id=SC, comment = {Is this sentence good?}]{Factor-level ordering} for each categorical variable will mirror that of the original analyses.
<!-- TR: don't know what you mean tbh; JVC: I get what you're saying, essentially we will keep the levels of their categorical variables the same when we refit the models, right? I changed it so that it says that. Change if wrong. -->
Each standardized (refitted) model will be fitted as a Bayesian regression model with Stan [@stan2021], RStan [@stan2020a], and brms [@burkner2017] in R [@R-base].
For those reported models that were originally fitted within a frequentist approach, uniform distributions will be used as the priors of all parameters (with the restriction that only positive numbers will be included for scale parameters), making the standardized models in fact equivalent to the reported frequentist models.
If a team has fitted Bayesian models, the same priors as reported by the team will be used in fitting the respective standardized model.

The estimated coefficients of the critical predictors (i.e. critical according to the analysis teams' self-reported inferential criteria), as obtained from the standardized models, will be used as the standardized effect size ($\eta_i$) of each reported model.
If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytic model (described in details in the next paragraph).
Moreover, to account for the differing degree of uncertainty around each standardized effect size, we will use the standard deviation of each effect size returned by the standardized models as the standard error ($\text{se}_i$) of the effect size.
This will enable us to fit a so-called "measurement-error" model, in which both the standardized effect sizes and their respective standard errors are entered in the meta-analytic model.
As a desired consequence, effect sizes with a greater standard error will be weighted less than those with a smaller standard error in the meta-analytic calculations.
